\textbf{{\Large {Recursive algorithm for the computation of branching coefficients of affine Lie algebras with applications in CFT}}}

### 2009-12-10 AffineLieAlgebras/InformalNotes/article.tex
Analysis of a_{\bot} for the embeddings a\subset g is almost completed, I need to add only a table.

\begin{document}
\title{\textbf{{\Large {Recurrent relation for branching coefficients of affine Lie algebras}}}}
\author{Vladimir Lyakhovsky\\
Theoretical Department, SPb State University,\\
198904, Sankt-Petersburg, Russia \\
e-mail:lyakh1507@nm.ru \\
[5mm] Anton Nazarov \\
%EndAName
Theoretical Department, SPb State University,\\
198904, Sankt-Petersburg, Russia \\
e-mail:antonnaz@gmail.com\\
}
\maketitle

@@

\section{Introduction}
\label{sec:introduction}

@@

The extended Dynkin diagram of $B_2$ 
\begin{figure}[ph]
  \centering
  \includegraphics[width=40mm]{B2_A1_diagram.pdf}
  \caption{Extended Dynkin diagram of $B_2$ and embedding of $A_1$}
  \label{fig:B2Dynkin}
\end{figure}
We then drop central node and get the embedding $A_1\oplus A_1\subset B_2$. Then $\mathfrak{a}=A_1$ and $\mathfrak{a}_{\bot}=A_1$.

Note that when we study the regular embedding obtained by the dropping of the nodes of the extended Dynkin diagram of the algebra $\mathfrak{g}$ and the subalgebra $\mathfrak{a}$ is one of the connected components, the subalgebra $\mathfrak{a}_{\bot}$ may be broader than the algebra generated by the other connected components. See for example the figure \ref{fig:dynkin} for the embedding of $B_2\subset B_4$. 
In this case the extended Dynkin diagram of $B_4$ is broken by the dropping of simple root $\alpha_2=e_2-e_3$ into the diagrams of the subalgebra of interest $\mathfrak{a}=B_2$ and two diagrams of the orthogonal $A_1$ subalgebras. But the subalgebra $\mathfrak{a}_{\bot}$ is equal not to $A_1\oplus A_1$ but to $B_2$. 
This fact is due to the existence of positive root $e_2=s_{\alpha_2}\cdot s_{\alpha_3}\cdot\alpha_4$ in the root system of $B_4$.

In the language of Weyl groups the task of construction of the root system of $\mathfrak{a}_{\bot}$ is formulated as follows. Given a Weyl group $W$ and a subgroup $W_{\mathfrak{a}}$ find the subgroup $W_{\mathfrak{a}_{\bot}}\subset W$ such that $\omega\, W_{\mathfrak{a}}\,\omega^{-1}=W_{\mathfrak{a}}; \;\text{for}\; \omega\in W_{\mathfrak{a}_{\bot}}$, so we need to find the normalizer of $W_{\mathfrak{a}}$ in $W$. This task can be carried out using the computational methods of finite group theory \cite{stembridge2001computational} but we are unaware of any publication with the exhaustive tables of such a subgroups.

In the case of special embeddings the set $\Delta^{+}_{\bot}$ can be empty as for the special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $A_1\subset A_2\subset A_3$ which is depicted at the Figure \ref{fig:a1a2a3}.
\begin{figure}[bh]
\noindent  \centering{
  \includegraphics[width=90mm]{special_A1_A2_A3.pdf}
  \caption{Special embedding $A_1\subset A_2\subset A_3$. Grey vectors are the roots of $A_2$, thick black - of $\mathfrak{a}=A_1$, dashed black are the orthogonal roots of $A_1$ which is contained in $\mathfrak{a}_{\bot}$ }
}
  \label{fig:a1a2a3}
\end{figure}

>>>>

\begin{document}
\title{\textbf{{\Large {Recursive algorithm for the computation of branching coefficients of affine Lie algebras with applications in CFT}}}}
\author{Vladimir Lyakhovsky\\
Theoretical Department, SPb State University,\\
198904, Sankt-Petersburg, Russia \\
e-mail:lyakh1507@nm.ru \\
[5mm] Anton Nazarov \\
%EndAName
Theoretical Department, SPb State University,\\
198904, Sankt-Petersburg, Russia \\
e-mail:antonnaz@gmail.com\\
}
\maketitle

@@

\newpage
\section{Introduction}
\label{sec:introduction}

@@

The extended Dynkin diagram of $B_2$ 
\begin{figure}[ph]
  \centering
  \includegraphics[width=50mm]{B2_A1_diagram.pdf}
  \caption{Extended Dynkin diagram of $B_2$ and embedding of $A_1$}
  \label{fig:B2Dynkin}
\end{figure}
We then drop central node and get the embedding $A_1\oplus A_1\subset B_2$. Then $\mathfrak{a}=A_1$ and $\mathfrak{a}_{\bot}=A_1$.

Here we give the simple criterion of $\Delta^{+}_{\bot}$'s non-emptiness for the regular embedding $\mathfrak{a}\subset \mathfrak{g}$ for simple $\mathfrak{a}$ and $\mathfrak{g}$. If Dynkin diagram of $\mathfrak{g}$ can be split into the unconnected diagrams of $\mathfrak{a}$ and some other subalgebras $\{\mathfrak{\bar{a}}_j\}$ then the subset $\Delta_{\bot}$ is non-empty, subalgebra $\mathfrak{a}_{\bot}$ is non-trivial and all the $\mathfrak{\bar{a}}_j$ are the subalgebras of $\mathfrak{a}_{\bot}$.

Note that when we study the regular embedding obtained by the dropping of the nodes of the extended Dynkin diagram of the algebra $\mathfrak{g}$ and the subalgebra $\mathfrak{a}$ is one of the connected components, the subalgebra $\mathfrak{a}_{\bot}$ may be broader than the algebra generated by the other connected components. See for example the figure \ref{fig:dynkin} for the embedding of $B_2\subset B_4$. 
In this case the extended Dynkin diagram of $B_4$ is split by dropping of simple root $\alpha_2=e_2-e_3$ into the diagrams of the subalgebra of interest $\mathfrak{a}=B_2$ and two diagrams of the orthogonal $A_1$ subalgebras. But the subalgebra $\mathfrak{a}_{\bot}$ is equal not to $A_1\oplus A_1$ but to $B_2$. 
This fact is due to the existence of positive root $e_2=s_{\alpha_2}\cdot s_{\alpha_3}\cdot\alpha_4$ in the root system of $B_4$.

We should analyze the case when the diagram of the subalgebra $\mathfrak{a}_{\bot}$ is not a subdiagram of the extended Dynkin diagram $\mathfrak{g}$ for the simple Lie algebras $\mathfrak{a},\,\mathfrak{g}$ and the regular embedding $\mathfrak{a}\subset \mathfrak{g}$.
 We drop the subdiagram of $\mathfrak{a}$ and the node $\alpha'$ that connects it with all the rest nodes of the diagram of $\mathfrak{g}$ and consider the remaining diagram. This diagram is the diagram of the algebra $\mathfrak{\bar{a}}$ of $\mathrm{rank}(\mathfrak{\bar{a}}) = \mathrm{rank}(\mathfrak{g})-\mathrm{rank}(\mathfrak{a})$. It is clear that $\mathfrak{\bar{a}}\subset \mathfrak{a}_{\bot}$. So the question is if $\mathfrak{a}_{\bot}$ has additional roots, which are not the roots of $\mathfrak{\bar{a}}$ but are the linear combinations of them. It is possible when the set of the angles between the roots of $\mathfrak{\bar{a}}$ does not contain all the angles between the roots of $\mathfrak{a}$, then reflecting the roots of $\mathfrak{a}$ by $s_{\alpha'}$ we the additional roots of $\mathfrak{a}_{\bot}$.

All the cases are listed in the following table.

\begin{tabular}{|l|l|}

\end{tabular}

In the language of Weyl groups the task of construction of the root system of $\mathfrak{a}_{\bot}$ is formulated as follows. Given a Weyl group $W$ and a subgroup $W_{\mathfrak{a}}$ find the subgroup $W_{\mathfrak{a}_{\bot}}\subset W$ such that $\omega\, W_{\mathfrak{a}}\,\omega^{-1}=W_{\mathfrak{a}}; \;\text{for}\; \omega\in W_{\mathfrak{a}_{\bot}}$, so we need to find the normalizer of $W_{\mathfrak{a}}$ in $W$, such that some of the elements of $W_{\mathfrak{a}_{\bot}}$ are the reflections corresponding to the positive roots of $\mathfrak{g}$. This task can be carried out using the computational methods of finite group theory \cite{stembridge2001computational} but we are unaware of any publication with the exhaustive tables of such a subgroups.

In the case of special embeddings the set $\Delta^{+}_{\bot}$ can be empty as for the special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $A_1\subset A_2\subset A_3$ which is depicted at the Figure \ref{fig:a1a2a3}.
\begin{figure}[ph]
\noindent  \centering{
  \includegraphics[width=120mm]{special_A1_A2_A3.pdf}
  \caption{Special embedding $A_1\subset A_2\subset A_3$. Grey vectors are the roots of $A_2$, thick black - of $\mathfrak{a}=A_1$, dashed black are the orthogonal roots of $A_1$ which is contained in $\mathfrak{a}_{\bot}$ }
}
  \label{fig:a1a2a3}
\end{figure}
